Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added network drawings.

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{training_overview.pdf}
  \caption{Overview over our framework, showing blocks existing (black) and components currently worked on (gray).}\label{fig:overview}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{block-diagram.pdf}
  \caption{Block diagram of the implementation, On the left the host code, and on the right side the device code. The host side orchestrates all the computation on the device side.}\label{fig:block-diagram}
\end{figure*}

@@

\subsection{Network Tested + Data-set}
The used example networks are a simple multi-layer perceptron.
So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.
These layers are often called ``Dense'' layers.
The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
So the data set provides \num{784} input features.
The structure of the sample MNIST network is.
\begin{enumerate}
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}
So in total a three layer network, or threes sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.

The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, so \num{3072} input features.
The structure of the sample CIFAR-10 network is.
\begin{enumerate}
  \item Dense(1024)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}

The data set was trained using the first \num{50000} images from the data set.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
The CPU code was implemented using the NumPy array.dot function.

\section{Results}\label{sec:result}
The host (NumPy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.

@@

>>>>

\begin{figure*}[p]
  \centering
  \includegraphics[width=0.7\linewidth]{training_overview.pdf}
  \caption{Overview over our framework, showing blocks existing (black) and components currently worked on (gray).}\label{fig:overview}
\end{figure*}

@@

\begin{figure*}[p]
  \centering
  \includegraphics[width=0.7\linewidth]{block-diagram.pdf}
  \caption{Block diagram of the implementation, on the left the host code, and on the right side the device code. The host side orchestrates all the computation on the device side.}\label{fig:block-diagram}
\end{figure*}

\begin{figure*}[p]
  \centering
  \includegraphics[width=0.6\linewidth]{mnist-network.pdf}
  \caption{MNIST sample network configuration}\label{fig:mnist-network}
\end{figure*}
\begin{figure*}[p]
  \centering
  \includegraphics[width=0.8\linewidth]{cifar10-network.pdf}
  \caption{CIFAR-10 sample network configuration}\label{fig:cifar10-network}
\end{figure*}

@@

\subsection{Network Tested + Data-set}
The used example networks are a multi-layer perceptron.
So all layers are an array neurons and every neuron is connected to every neuron in the next layer.
These layers are often called ``Dense'' layers.
The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
So the data set provides \num{784} input features.
The structure of the sample MNIST network is shown in \cref{fig:mnist-network}.
In total a three layer network plus the input layer, or three sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.\\
The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, so \num{3072} input features.
The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.\\
The data set was trained using the first \num{50000} images from the data set.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
The CPU code was implemented using the NumPy array.dot function.

\section{Results}\label{sec:result}
The host (NumPy based) code benchmarked at \num{60} GFLOPS for straight-forward inference of the first network and about \num{160} GFLOPS for the second network.
A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.

@@

\section{Acknowledgment}\label{sec:acknowledgment}
%TODO
